Spontaneous Similarity Judgments of Musical Tones played with various Playing Techniques

### 2017-12-08 paper/lagrangeSpontaneousSimilarity2017.tex
dendrogram

Considering not only the type of musical instrument but also the playing technique is interesting in that matter, as it invite us to consider the relation between the rate of modulation and timbre percepts. A notion that have not been extensively studied in the litterature. It also permits to consider the notion of timbral similarity at finer grain of detail.

The contributions of the paper are as follows: 1) provide perceptual data that account for the perception of musical tones played with various playing techniques, 2), demonstrate that, for the gathered data, the type of playing technique plays an important role for the organization of the data, and 3) propose a perceptually motivated computational model of timbre perception that account well for the human judgments studied in this paper.

\section{Experiment 1}\label{sec:}

@@

\section{Experiment 2}\label{sec:}

@@

\section{Analysis}\label{sec:}

@@

We therefore now only study the properties of the groupings performed by the subject prior converting them into an overall similarity matrix.

Among the 20 colors available, the subjects used on average \ml{fill}. The distribution of the number of groups can be seen on Figure \ref{fig:xp2nbGroup}. The size of the groups is on average \ml{fill}. The distribution of the size of groups can be seen on Figure \ref{fig:xp2sizeGroup}.

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example.png}
\caption{Histogram of the number of groups.}
\label{fig:xp2nbGroup}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example.png}
\caption{Histogram of the size of groups.}
\label{fig:xp2sizeGroup}
\end{figure}

@@

\section{Model}\label{sec:}

\section{Results}\label{sec:}

\section{Discussion}\label{sec:}

>>>>

Considering not only the type of musical instrument but also the playing technique is interesting in that matter, as it invite us to consider the relation between the rate of modulation and timbre percepts. A notion that have not been extensively studied in the litterature. Compared to instrument class, the reference that is usually taken in timbre studies, it also permits to consider the notion of timbral similarity at finer grain of detail.

The contributions of the paper are as follows: 1) provide perceptual data that account for the perception of musical tones played with various playing techniques, 2), demonstrate that, for the gathered data, the type of playing technique plays an important role in the spontaneous judgments of similarity, and 3) propose a perceptually motivated computational model of timbre perception that account well for the human judgments studied in this paper.

\section{Experiment 1}\label{sec:xp1}

@@

\section{Experiment 2}\label{sec:xp2}

@@

\section{Analysis}\label{sec:analysis}

@@

We therefore now only study the properties of the groupings performed by the subject prior to converting them into an overall similarity matrix.

Among the 20 colors available, the subjects used on average $10.2 \pm  4.1$ different colors to group \ipt. The distribution of the number of groups can be seen on Figure \ref{fig:xp2nbGroup}. The size of the groups is on average $7.7 \pm   7.2$. The distribution of the size of groups can be seen on Figure \ref{fig:xp2sizeGroup}. The large number of small groups indicates that many subjects considered that a few of the \ipt were very different from all the remaining \ipt.

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/nbc.png}
\caption{Histogram of the number of groups.}
\label{fig:xp2nbGroup}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/sbc.png}
\caption{Histogram of the size of groups.}
\label{fig:xp2sizeGroup}
\end{figure}

@@

\section{Model}\label{sec:model}

\section{Results}\label{sec:results}

\section{Discussion}\label{sec:discussion}
